---
title: "augmentation PK tacro coeur"
author: "jbw + cb"
date: "2023-12-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

loading of packages

```{r}
library(tidyverse)
library(tidymodels)
library(FNN)
library(ggcorrplot)
library(GGally)
library(patchwork)
```
Evaluation number of data with not exact time for which time had to be rounded to the closest time

```{r}
# library(readr)
# tac_coeur_a_changer <- read_csv("C:/Users/woillp01/Desktop/MPA_data_augmentation_pk/tac_coeur_a_changer.csv") 
# 
# tac_coeur_a_changer %>% mutate(TIME = as.factor(TIME)) %>% count(TIME) %>% filter(n<20) %>% summarise(sum_n = sum(n)/nrow(tac_coeur_a_changer))

```


loading of the data

```{r}
# 
library(readr)
original_pk <- read_delim("tacro_coeur_pour_augmentation.csv", 
                       delim = ",", escape_double = FALSE, 
                       trim_ws = TRUE) %>% 
  mutate(Visite = parse_number(Visite)) %>% 
  select(-id) %>% 
  drop_na(starts_with("conc_"))
summary(original_pk)
str(original_pk)


original_pk_long <- original_pk %>% 
  mutate(id = c(30:58)) %>% 
  pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
  mutate(time = as.numeric(time)) %>% 
  arrange(Visite, DOSE,AGE, time)
```

export original long and wide

```{r}
#export for clement
write_csv(original_pk, file = "original_pk.csv")
write_csv(original_pk_long, file = "tacro_coeur_original_pk_long.csv")
```

# Algorithm with knn=5

```{r}

data_normalized <- scale(original_pk)
pca <- prcomp(data_normalized, scale. = FALSE)# pour selecitonner le nombre de cp rank. = 3
# Number of neighbors
k <- 5  # Adjust this based on your requirement
pca_transformed_data <- pca$x
knn_result <- get.knn(pca_transformed_data, k)

generate_avatar_weights <- function(knn_result, pca_transformed_data, k) {
  n <- nrow(pca_transformed_data)
  avatar_weights <- matrix(nrow = n, ncol = k)
  
  for (i in 1:n) {
    # Step 1: Inverse of Distances
    distances <- sqrt(rowSums((pca_transformed_data[knn_result$nn.index[i, ], ] - pca_transformed_data[i, ])^2))
    inverse_distances <- 1 / distances
    
    # Step 2: Random Weights
    set.seed(12345)
    random_weights <- rexp(k, rate = 1)
    
    # Step 3: Contribution Factors
    set.seed(12345)
    shuffled_indices <- sample(k)
    contribution_factors <- 1 / (2^shuffled_indices)
    
    # Step 4: Calculate Weights
    weights <- inverse_distances * random_weights * contribution_factors
    
    # Step 5: Normalize Weights
    normalized_weights <- weights / sum(weights)
    
    avatar_weights[i, ] <- normalized_weights
  }
  
  return(avatar_weights)
}



# Generate avatar weights
avatar_weights <- generate_avatar_weights(knn_result, pca_transformed_data, k)

# Assuming pca_result, avatar_weights, knn_result$nn.index, and pca_transformed_data are already defined

# Function to generate avatars in PCA space based on weights
generate_avatars_pca_space <- function(pca_transformed_data, knn_indices, weights) {
  n <- nrow(pca_transformed_data)
  avatars_pca <- matrix(nrow = n, ncol = ncol(pca_transformed_data))
  
  for (i in 1:n) {
    weighted_avatars <- pca_transformed_data[knn_indices[i, ], ] * weights[i, ]
    avatars_pca[i, ] <- colSums(weighted_avatars)
  }
  
  return(avatars_pca)
}
# Generate avatars in PCA space
avatars_pca_space <- generate_avatars_pca_space(pca_transformed_data, knn_result$nn.index, avatar_weights)

# Assuming 'aids_pca' is the PCA object and 'avatars_pca_space' contains the avatars in PCA space
# Inverse PCA transformation
inverse_pca <- function(pca_object, pca_data) {
  return(pca_data %*% t(pca_object$rotation) + matrix(pca_object$center, nrow = nrow(pca_data), ncol = ncol(pca_object$rotation), byrow = TRUE))
}
avatars_original_scale <- inverse_pca(pca, avatars_pca_space)

# Assuming 'aids_data_normalized' contains the scaling attributes of the original data
# Inverse normalization (if the original data was normalized)
avatars_rescaled <- scale(avatars_original_scale, center = FALSE, scale = 1/attr(data_normalized, "scaled:scale"))
avatars_rescaled <- sweep(avatars_rescaled, 2, attr(data_normalized, "scaled:center"), "+")

avatars_tibble_knn5 <- as_tibble(avatars_rescaled) %>% 
  mutate(
    Visite = round(Visite, digits=0),
    DOSE  = round(DOSE, digits=0.25),
    AGE   = round(AGE , digits=0),
    SEX   = if_else(SEX>0.7 ,1,0),
    CYP3A5   = if_else(CYP3A5>0.2,1,0))
```

Plot of the synthetic and original in the latent space

```{r}
# Combine original and synthetic data for visualization
combined_data <- rbind(
  original_pk %>% mutate(DataType = 'Original'),
  avatars_tibble_knn5 %>% mutate(DataType = 'Synthetic')
)

# Perform PCA on combined data
combined_data_normalized <- scale(combined_data[, -which(names(combined_data) %in% c("DataType", "id"))])
combined_pca <- prcomp(combined_data_normalized, scale. = FALSE)

# Extract the first two principal components
combined_pca_data <- data.frame(combined_pca$x[, 1:2])
combined_pca_data$DataType <- combined_data$DataType

# Plot PCA with color differentiation
ggplot(combined_pca_data, aes(x = PC1, y = PC2, color = DataType)) +
  geom_point(alpha = 1) +
  theme_minimal() +
  labs(title = "PCA Plot", x = "Principal Component 1", y = "Principal Component 2", color = "Data Type")

```

## Compare the data

### summary distribution
```{r}
summary(avatars_tibble_knn5)
summary(original_pk)
```

Plot relationship C0 and CYP3A5

```{r}
original_pk %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
  geom_boxplot() +
  labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Original") +
  theme_bw()

avatars_tibble_knn5 %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
  geom_boxplot() +
  labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Synthetic") +
  theme_bw()
```


### plot correlation
```{r}

##Correlation Analysis
  cor_real <- cor(original_pk, use = "complete.obs")
  cor_synthetic <- cor(avatars_tibble_knn5, use = "complete.obs")
  
# plots
ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
           lab = TRUE,  pch.cex = 5,
  tl.cex = 6, lab_size = 2)
# plots
ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
           lab = TRUE,  pch.cex = 5,
  tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
group_comparison <-
   original_pk %>% 
  mutate(group="original") %>% 
  bind_rows(avatars_tibble_knn5 %>% 
              mutate(group="synthetic")) 

pm <- group_comparison %>% ggpairs(
  ggplot2::aes(colour = group,alpha = 0.5),
  upper = list(continuous = wrap("cor", size = 1.5)),
  lower=list(combo=wrap("facethist", binwidth=0.5))) + 
  theme(strip.text.x = element_text(size = 5),
           strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
pm
ggsave("comparaison_distribution_PK_knn5.pdf")

```

Process and plot the data

```{r}
avatar_knn5 <- avatars_tibble_knn5 %>%
  mutate(id = 1:nrow(avatars_tibble_knn5)) %>% 
  pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
  mutate(time = as.numeric(time)) %>% 
  arrange(id, time) %>% 
  relocate(id)

```

Plot the data

```{r}
original_pk_long %>% mutate(group="original") %>% 
  bind_rows(avatar_knn5 %>% mutate(group="synthetic")) %>% 
              ggplot(aes(x = time, y = DV, color = group)) + geom_point() +
  geom_point(alpha = 0.2, size = 3) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw()


original_pk_long %>% mutate(group="original") %>% 
  bind_rows(avatar_knn5 %>% 
              mutate(group="synthetic")) %>% 
  mutate(id = as.factor(id)) %>% 
  ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
  geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw() + facet_wrap(~group)
```


Export long and wide
```{r}
write_csv(avatar_knn5, file = "tacro_coeur_synthetic_knn5.csv")
write_csv(avatars_tibble_knn5, file = "wide_tacro_coeur_synthetic_knn5.csv")

```


# Algorithm with knn = 15

```{r}
# algroithm with knn=15
data_normalized <- scale(original_pk)
pca <- prcomp(data_normalized, scale. = FALSE)# pour selecitonner le nombre de cp rank. = 3
# Number of neighbors
k <- 15  # Adjust this based on your requirement
pca_transformed_data <- pca$x
knn_result <- get.knn(pca_transformed_data, k)

generate_avatar_weights <- function(knn_result, pca_transformed_data, k) {
  n <- nrow(pca_transformed_data)
  avatar_weights <- matrix(nrow = n, ncol = k)
  
  for (i in 1:n) {
    # Step 1: Inverse of Distances
    distances <- sqrt(rowSums((pca_transformed_data[knn_result$nn.index[i, ], ] - pca_transformed_data[i, ])^2))
    inverse_distances <- 1 / distances
    
    # Step 2: Random Weights
    set.seed(12)
    random_weights <- rexp(k, rate = 1)
    
    # Step 3: Contribution Factors
    set.seed(12)
    shuffled_indices <- sample(k)
    contribution_factors <- 1 / (2^shuffled_indices)
    
    # Step 4: Calculate Weights
    weights <- inverse_distances * random_weights * contribution_factors
    
    # Step 5: Normalize Weights
    normalized_weights <- weights / sum(weights)
    
    avatar_weights[i, ] <- normalized_weights
  }
  
  return(avatar_weights)
}



# Generate avatar weights
avatar_weights <- generate_avatar_weights(knn_result, pca_transformed_data, k)

# Assuming pca_result, avatar_weights, knn_result$nn.index, and pca_transformed_data are already defined

# Function to generate avatars in PCA space based on weights
generate_avatars_pca_space <- function(pca_transformed_data, knn_indices, weights) {
  n <- nrow(pca_transformed_data)
  avatars_pca <- matrix(nrow = n, ncol = ncol(pca_transformed_data))
  
  for (i in 1:n) {
    weighted_avatars <- pca_transformed_data[knn_indices[i, ], ] * weights[i, ]
    avatars_pca[i, ] <- colSums(weighted_avatars)
  }
  
  return(avatars_pca)
}
# Generate avatars in PCA space
avatars_pca_space <- generate_avatars_pca_space(pca_transformed_data, knn_result$nn.index, avatar_weights)

# Assuming 'aids_pca' is the PCA object and 'avatars_pca_space' contains the avatars in PCA space
# Inverse PCA transformation
inverse_pca <- function(pca_object, pca_data) {
  return(pca_data %*% t(pca_object$rotation) + matrix(pca_object$center, nrow = nrow(pca_data), ncol = ncol(pca_object$rotation), byrow = TRUE))
}
avatars_original_scale <- inverse_pca(pca, avatars_pca_space)

# Assuming 'aids_data_normalized' contains the scaling attributes of the original data
# Inverse normalization (if the original data was normalized)
avatars_rescaled <- scale(avatars_original_scale, center = FALSE, scale = 1/attr(data_normalized, "scaled:scale"))
avatars_rescaled <- sweep(avatars_rescaled, 2, attr(data_normalized, "scaled:center"), "+")

avatars_tibble_knn15 <- as_tibble(avatars_rescaled) %>% 
  mutate(
    Visite = round(Visite, digits=0),
    DOSE  = round(DOSE, digits=0.25),
    AGE   = round(AGE , digits=0),
    SEX   = round(SEX , digits=0),
    CYP3A5   = round(CYP3A5, digits=0))

```


## Compare the data

### summary dsitribution
```{r}
summary(avatars_tibble_knn15)
summary(original_pk)
```



### plot correlation
```{r}

##Correlation Analysis
  cor_real <- cor(original_pk, use = "complete.obs")
  cor_synthetic <- cor(avatars_tibble_knn15, use = "complete.obs")
  
# plots
ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
           lab = TRUE,  pch.cex = 5,
  tl.cex = 6, lab_size = 2)
# plots
ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
           lab = TRUE,  pch.cex = 5,
  tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
group_comparison <-
   original_pk %>% 
  mutate(group="original") %>% 
  bind_rows(avatars_tibble_knn15 %>% 
              mutate(group="synthetic")) 

pm <- group_comparison %>% ggpairs(
  ggplot2::aes(colour = group,alpha = 0.5),
  upper = list(continuous = wrap("cor", size = 1.5)),
  lower=list(combo=wrap("facethist", binwidth=0.5))) + 
  theme(strip.text.x = element_text(size = 5),
           strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
pm
ggsave("comparaison_distribution_PK_knn15.pdf")

```

Process and plot the data

```{r}
avatar_knn15 <- avatars_tibble_knn15 %>% 
   mutate(id = 1:nrow(avatars_tibble_knn15)) %>% 
  pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
  mutate(time = as.numeric(time)) %>% 
  arrange(Visite, DOSE,AGE, time)
original_pk_long <- original_pk %>%
    mutate(id = c(30:58)) %>% 
  pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
  mutate(time = as.numeric(time)) %>% 
  arrange(Visite, DOSE,AGE, time)

original_pk_long %>% mutate(group="original") %>% 
  bind_rows(avatar_knn15 %>% mutate(group="synthetic")) %>% 
  ggplot(aes(x = time, y = DV, color = group)) + geom_point()+
  geom_point(alpha = 0.2, size = 3) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw()

original_pk_long %>% mutate(group="original") %>% 
  bind_rows(avatar_knn15 %>% 
              mutate(group="synthetic")) %>% 
  mutate(id = as.factor(id)) %>% 
  ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
  geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw() + facet_wrap(~group)

```

Export wide and long data

```{r}
write_csv(avatar_knn15, file = "tacro_coeur_synthetic_knn15.csv")
write_csv(avatars_tibble_knn15, file = "wide_tacro_coeur_synthetic_knn15.csv")

```

# Data augmentation knn = 5

```{r}
# ## data augmentation knn5
# data_augment_avatar <- function(x) {
#   data_normalized <- scale(original_pk)
#   pca <- prcomp(data_normalized, scale. = FALSE)# pour selecitonner le nombre de cp rank. = 3
#   # Number of neighbors
#   k <- 5  # Adjust this based on your requirement
#   pca_transformed_data <- pca$x
#   knn_result <- get.knn(pca_transformed_data, k)
#   
#   generate_avatar_weights <- function(knn_result, pca_transformed_data, k) {
#     n <- nrow(pca_transformed_data)
#     avatar_weights <- matrix(nrow = n, ncol = k)
#     
#     for (i in 1:n) {
#       # Step 1: Inverse of Distances
#       distances <- sqrt(rowSums((pca_transformed_data[knn_result$nn.index[i, ], ] - pca_transformed_data[i, ])^2))
#       inverse_distances <- 1 / distances
#       
#       # Step 2: Random Weights
#       set.seed( str_c(1,x))
#       random_weights <- rexp(k, rate = 1)
#       
#       # Step 3: Contribution Factors
#       set.seed( str_c(1,x))
#       shuffled_indices <- sample(k)
#       contribution_factors <- 1 / (2^shuffled_indices)
#       
#       # Step 4: Calculate Weights
#       weights <- inverse_distances * random_weights * contribution_factors
#       
#       # Step 5: Normalize Weights
#       normalized_weights <- weights / sum(weights)
#       
#       avatar_weights[i, ] <- normalized_weights
#     }
#     
#     return(avatar_weights)
#   }
#   
#   
#   
#   # Generate avatar weights
#   avatar_weights <- generate_avatar_weights(knn_result, pca_transformed_data, k)
#   
#   # Assuming pca_result, avatar_weights, knn_result$nn.index, and pca_transformed_data are already defined
#   
#   # Function to generate avatars in PCA space based on weights
#   generate_avatars_pca_space <- function(pca_transformed_data, knn_indices, weights) {
#     n <- nrow(pca_transformed_data)
#     avatars_pca <- matrix(nrow = n, ncol = ncol(pca_transformed_data))
#     
#     for (i in 1:n) {
#       weighted_avatars <- pca_transformed_data[knn_indices[i, ], ] * weights[i, ]
#       avatars_pca[i, ] <- colSums(weighted_avatars)
#     }
#     
#     return(avatars_pca)
#   }
#   # Generate avatars in PCA space
#   avatars_pca_space <- generate_avatars_pca_space(pca_transformed_data, knn_result$nn.index, avatar_weights)
#   # Assuming 'aids_pca' is the PCA object and 'avatars_pca_space' contains the avatars in PCA space
#   # Inverse PCA transformation
#   inverse_pca <- function(pca_object, pca_data) {
#     return(pca_data %*% t(pca_object$rotation) + matrix(pca_object$center, nrow = nrow(pca_data), ncol = ncol(pca_object$rotation), byrow = TRUE))
#   }
#   avatars_original_scale <- inverse_pca(pca, avatars_pca_space)
#   
#   # Assuming 'aids_data_normalized' contains the scaling attributes of the original data
#   # Inverse normalization (if the original data was normalized)
#   avatars_rescaled <- scale(avatars_original_scale, center = FALSE, scale = 1/attr(data_normalized, "scaled:scale"))
#   avatars_rescaled <- sweep(avatars_rescaled, 2, attr(data_normalized, "scaled:center"), "+")
#   
#   avatars_tibble <- as_tibble(avatars_rescaled) %>% 
#   mutate(
#     Visite = round(Visite, digits=0),
#     DOSE  = round(DOSE, digits=0.25),
#     AGE   = round(AGE , digits=0),
#     SEX   = if_else(SEX>0.7 ,1,0),
#     CYP3A5   = if_else(CYP3A5>0.2,1,0))
# }
# 
# iteration <- c(1:4)
# 
# augmented_data_5 <- map_dfr(iteration, data_augment_avatar, .id = "iter_")
```

## Compare the data

### summary dsitribution
```{r}
# summary(augmented_data_5)
# summary(original_pk)
```



### plot correlation
```{r}

# ##Correlation Analysis
#   cor_real <- cor(original_pk, use = "complete.obs")
#   cor_synthetic <- cor(augmented_data_5 %>% select(-iter_), use = "complete.obs")
#   
# # plots
# ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
# # plots
# ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
# group_comparison <-
#    original_pk %>% 
#   mutate(group="original") %>% 
#   bind_rows(augmented_data_5 %>% 
#               mutate(group="synthetic")) %>% 
#   select(-iter_)
# 
# pm <- group_comparison %>% ggpairs(
#   ggplot2::aes(colour = group,alpha = 0.5),
#   upper = list(continuous = wrap("cor", size = 1.5)),
#   lower=list(combo=wrap("facethist", binwidth=0.5))) + 
#   theme(strip.text.x = element_text(size = 5),
#            strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
# pm
# ggsave("comparaison_distribution_PK_augmented_knn5.pdf")

```

Process and plot the data

```{r}
# avatar_augmented_knn5 <- augmented_data_5 %>% 
#     mutate(id = 1:nrow(augmented_data_5)) %>% 
#   pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
#   mutate(time = as.numeric(time)) %>% 
#   arrange(Visite, DOSE,AGE, time)
# original_pk_long <- original_pk %>% 
#    mutate(id = c(30:58)) %>% 
#   pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
#   mutate(time = as.numeric(time)) %>% 
#   arrange(Visite, DOSE,AGE, time)

```

Plots
```{r}
# ## plots
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(avatar_augmented_knn5 %>% mutate(group="synthetic")) %>% 
#   ggplot(aes(x = time, y = DV, color = group)) + 
#   geom_point(alpha = 0.2, size = 3) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw()
# 
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(avatar_augmented_knn5 %>% 
#               mutate(group="synthetic")) %>% 
#   mutate(id = as.factor(id)) %>% 
#   ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
#   geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw() + facet_wrap(~group)
```


Export long and wide

```{r}
# write_csv(avatar_augmented_knn5, file = "tacro_coeur_synthetic_augmented_knn5.csv")
# write_csv(augmented_data_5, file = "wide_tacro_coeur_synthetic_augmented_knn5.csv")
```

# Data augmentation knn = 15

```{r}
# ## data augmentation knn5
# data_augment_avatar <- function(x) {
#   data_normalized <- scale(original_pk)
#   pca <- prcomp(data_normalized, scale. = FALSE)# pour selecitonner le nombre de cp rank. = 3
#   # Number of neighbors
#   k <- 15  # Adjust this based on your requirement
#   pca_transformed_data <- pca$x
#   knn_result <- get.knn(pca_transformed_data, k)
#   
#   generate_avatar_weights <- function(knn_result, pca_transformed_data, k) {
#     n <- nrow(pca_transformed_data)
#     avatar_weights <- matrix(nrow = n, ncol = k)
#     
#     for (i in 1:n) {
#       # Step 1: Inverse of Distances
#       distances <- sqrt(rowSums((pca_transformed_data[knn_result$nn.index[i, ], ] - pca_transformed_data[i, ])^2))
#       inverse_distances <- 1 / distances
#       
#       # Step 2: Random Weights
#       set.seed( str_c(1,x))
#       random_weights <- rexp(k, rate = 1)
#       
#       # Step 3: Contribution Factors
#       set.seed( str_c(1,x))
#       shuffled_indices <- sample(k)
#       contribution_factors <- 1 / (2^shuffled_indices)
#       
#       # Step 4: Calculate Weights
#       weights <- inverse_distances * random_weights * contribution_factors
#       
#       # Step 5: Normalize Weights
#       normalized_weights <- weights / sum(weights)
#       
#       avatar_weights[i, ] <- normalized_weights
#     }
#     
#     return(avatar_weights)
#   }
#   
#   
#   
#   # Generate avatar weights
#   avatar_weights <- generate_avatar_weights(knn_result, pca_transformed_data, k)
#   
#   # Assuming pca_result, avatar_weights, knn_result$nn.index, and pca_transformed_data are already defined
#   
#   # Function to generate avatars in PCA space based on weights
#   generate_avatars_pca_space <- function(pca_transformed_data, knn_indices, weights) {
#     n <- nrow(pca_transformed_data)
#     avatars_pca <- matrix(nrow = n, ncol = ncol(pca_transformed_data))
#     
#     for (i in 1:n) {
#       weighted_avatars <- pca_transformed_data[knn_indices[i, ], ] * weights[i, ]
#       avatars_pca[i, ] <- colSums(weighted_avatars)
#     }
#     
#     return(avatars_pca)
#   }
#   # Generate avatars in PCA space
#   avatars_pca_space <- generate_avatars_pca_space(pca_transformed_data, knn_result$nn.index, avatar_weights)
#   # Assuming 'aids_pca' is the PCA object and 'avatars_pca_space' contains the avatars in PCA space
#   # Inverse PCA transformation
#   inverse_pca <- function(pca_object, pca_data) {
#     return(pca_data %*% t(pca_object$rotation) + matrix(pca_object$center, nrow = nrow(pca_data), ncol = ncol(pca_object$rotation), byrow = TRUE))
#   }
#   avatars_original_scale <- inverse_pca(pca, avatars_pca_space)
#   
#   # Assuming 'aids_data_normalized' contains the scaling attributes of the original data
#   # Inverse normalization (if the original data was normalized)
#   avatars_rescaled <- scale(avatars_original_scale, center = FALSE, scale = 1/attr(data_normalized, "scaled:scale"))
#   avatars_rescaled <- sweep(avatars_rescaled, 2, attr(data_normalized, "scaled:center"), "+")
#   
#   avatars_tibble <- as_tibble(avatars_rescaled) %>% 
#   mutate(
#     Visite = round(Visite, digits=0),
#     DOSE  = round(DOSE, digits=0.25),
#     AGE   = round(AGE , digits=0),
#     SEX   = if_else(SEX>0.7 ,1,0),
#     CYP3A5   = if_else(CYP3A5>0.2,1,0))
# }
# 
# iteration <- c(1:4)
# 
# augmented_data_15 <- map_dfr(iteration, data_augment_avatar, .id = "iter_")
```

## Compare the data

### summary dsitribution
```{r}
# summary(augmented_data_15)
# summary(original_pk)
```



### plot correlation
```{r}

# ##Correlation Analysis
#   cor_real <- cor(original_pk, use = "complete.obs")
#   cor_synthetic <- cor(augmented_data_15 %>% select(-iter_), use = "complete.obs")
#   
# # plots
# ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 15,
#   tl.cex = 6, lab_size = 2)
# # plots
# ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 15,
#   tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
# group_comparison <-
#    original_pk %>% 
#   mutate(group="original") %>% 
#   bind_rows(augmented_data_15 %>% 
#               mutate(group="synthetic")) %>% 
#   select(-iter_)
# 
# pm <- group_comparison %>% ggpairs(
#   ggplot2::aes(colour = group,alpha = 0.5),
#   upper = list(continuous = wrap("cor", size = 1.5)),
#   lower=list(combo=wrap("facethist", binwidth=0.5))) + 
#   theme(strip.text.x = element_text(size = 5),
#            strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
# pm
# ggsave("comparaison_distribution_PK_augmented_knn15.pdf")

```

Process and plot the data

```{r}
# avatar_augmented_knn15 <- augmented_data_15 %>% 
#     mutate(id = 1:nrow(augmented_data_15)) %>% 
#   pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
#   mutate(time = as.numeric(time)) %>% 
#   arrange(Visite, DOSE,AGE, time)
# original_pk_long <- original_pk %>% 
#    mutate(id = c(30:58)) %>% 
#   pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
#   mutate(time = as.numeric(time)) %>% 
#   arrange(Visite, DOSE,AGE, time)

```

Plots
```{r}
# ## plots
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(avatar_augmented_knn15 %>% mutate(group="synthetic")) %>% 
#   ggplot(aes(x = time, y = DV, color = group)) + 
#   geom_point(alpha = 0.2, size = 3) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw()
# 
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(avatar_augmented_knn15 %>% 
#               mutate(group="synthetic")) %>% 
#   mutate(id = as.factor(id)) %>% 
#   ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
#   geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw() + facet_wrap(~group)
```


Export long and wide

```{r}
# write_csv(avatar_augmented_knn15, file = "tacro_coeur_synthetic_augmented_knn15.csv")
# write_csv(augmented_data_15, file = "wide_tacro_coeur_synthetic_augmented_knn15.csv")
```


# Tabular Variational Auto-Encoder (TVAE)

## Non augmented data

### load the data

```{r}
tvae <- read_csv("GAN_sortie_anonymisation240108/pkpop_tvae_data_v240108.dat")
```


### summary distribution
```{r}
summary(tvae)
summary(original_pk)
```

Plot relationship C0 and CYP3A5

```{r}
original_pk %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
  geom_boxplot() +
  labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Original") +
  theme_bw()

tvae %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
  geom_boxplot() +
  labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Synthetic") +
  theme_bw()
```


### plot correlation
```{r}

##Correlation Analysis
  cor_real <- cor(original_pk, use = "complete.obs")
  cor_synthetic <- cor(tvae %>% select(-SEX), use = "complete.obs")
  
# plots
ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
           lab = TRUE,  pch.cex = 5,
  tl.cex = 6, lab_size = 2)
# plots
ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
           lab = TRUE,  pch.cex = 5,
  tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
group_comparison <-
   original_pk %>% 
  mutate(group="original") %>% 
  bind_rows(tvae %>% 
              mutate(group="synthetic")) 

pm <- group_comparison %>% ggpairs(
  ggplot2::aes(colour = group,alpha = 0.5),
  upper = list(continuous = wrap("cor", size = 1.5)),
  lower=list(combo=wrap("facethist", binwidth=0.5))) + 
  theme(strip.text.x = element_text(size = 5),
           strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
pm
ggsave("comparaison_distribution_PK_tvae.pdf")

```

Process and plot the data

```{r}
tvae_long <- tvae %>%
  mutate(id = 1:nrow(tvae)) %>% 
  pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
  mutate(time = as.numeric(time)) %>% 
  arrange(id, time) %>% 
  relocate(id)

```

Plot the data

```{r}
original_pk_long %>% mutate(group="original") %>% 
  bind_rows(tvae_long %>% mutate(group="synthetic")) %>% 
              ggplot(aes(x = time, y = DV, color = group)) + geom_point() +
  geom_point(alpha = 0.2, size = 3) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw()


original_pk_long %>% mutate(group="original") %>% 
  bind_rows(tvae_long %>% 
              mutate(group="synthetic")) %>% 
  mutate(id = as.factor(id)) %>% 
  ggplot(aes(x = time, y = log(DV), color = id)) +  geom_line(show.legend = FALSE)+
  geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw() + facet_wrap(~group)
```


Export long and wide
```{r}
write_csv(tvae_long, file = "tacro_coeur_synthetic_tvae.csv")
write_csv(tvae, file = "wide_tacro_coeur_synthetic_tvae.csv")

```

## Augmented data

### load the data

```{r}
# tvae_augmented <- read_csv("GAN_sortie_anonymisation240108/pkpop_tvae_data_large_v240108.dat")
```


### summary distribution
```{r}
# summary(tvae_augmented)
# summary(original_pk)
```

Plot relationship C0 and CYP3A5

```{r}
# original_pk %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
#   geom_boxplot() +
#   labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Original") +
#   theme_bw()
# 
# tvae_augmented %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
#   geom_boxplot() +
#   labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Synthetic") +
#   theme_bw()
```


### plot correlation
```{r}

# ##Correlation Analysis
#   cor_real <- cor(original_pk, use = "complete.obs")
#   cor_synthetic <- cor(tvae_augmented %>% select(-SEX), use = "complete.obs")
#   
# # plots
# ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
# # plots
# ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
# group_comparison <-
#    original_pk %>% 
#   mutate(group="original") %>% 
#   bind_rows(tvae_augmented %>% 
#               mutate(group="synthetic")) 
# 
# pm <- group_comparison %>% ggpairs(
#   ggplot2::aes(colour = group,alpha = 0.5),
#   upper = list(continuous = wrap("cor", size = 1.5)),
#   lower=list(combo=wrap("facethist", binwidth=0.5))) + 
#   theme(strip.text.x = element_text(size = 5),
#            strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
# pm
# ggsave("comparaison_distribution_PK_tvae_augmented.pdf")

```

Process and plot the data

```{r}
# tvae_augmented_long <- tvae_augmented %>%
#   mutate(id = 1:nrow(tvae_augmented)) %>% 
#   pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
#   mutate(time = as.numeric(time)) %>% 
#   arrange(id, time) %>% 
#   relocate(id)

```

Plot the data

```{r}
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(tvae_augmented_long %>% mutate(group="synthetic")) %>% 
#               ggplot(aes(x = time, y = DV, color = group)) + geom_point() +
#   geom_point(alpha = 0.2, size = 3) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw()
# 
# 
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(tvae_augmented_long %>% 
#               mutate(group="synthetic")) %>% 
#   mutate(id = as.factor(id)) %>% 
#   ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
#   geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw() + facet_wrap(~group)
```


Export long and wide
```{r}
# write_csv(tvae_augmented_long, file = "tacro_coeur_synthetic_tvae_augmented.csv")
# write_csv(tvae_augmented, file = "wide_tacro_coeur_synthetic_tvae_augmented.csv")

```


# Conditionnal Tabular Generative Adversial Network (CTGAN)

## Non augmented data

### load the data

```{r}
ctgan <- read_csv("GAN_sortie_anonymisation240108/pkpop_ctgan_data_v240108.dat")
```


### summary distribution
```{r}
summary(ctgan)
summary(original_pk)
```

Plot relationship C0 and CYP3A5

```{r}
original_pk %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
  geom_boxplot() +
  labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Original") +
  theme_bw()

ctgan %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
  geom_boxplot() +
  labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Synthetic") +
  theme_bw()
```


### plot correlation
```{r}

# ##Correlation Analysis
#   cor_real <- cor(original_pk, use = "complete.obs")
#   cor_synthetic <- cor(ctgan %>% select(-SEX), use = "complete.obs")
#   
# # plots
# ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
# # plots
# ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
group_comparison <-
   original_pk %>% 
  mutate(group="original") %>% 
  bind_rows(ctgan %>% 
              mutate(group="synthetic")) 

pm <- group_comparison %>% ggpairs(
  ggplot2::aes(colour = group,alpha = 0.5),
  upper = list(continuous = wrap("cor", size = 1.5)),
  lower=list(combo=wrap("facethist", binwidth=0.5))) + 
  theme(strip.text.x = element_text(size = 5),
           strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
pm
ggsave("comparaison_distribution_PK_ctgan.pdf")

```

Process and plot the data

```{r}
ctgan_long <- ctgan %>%
  mutate(id = 1:nrow(ctgan)) %>% 
  pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
  mutate(time = as.numeric(time)) %>% 
  arrange(id, time) %>% 
  relocate(id)

```

Plot the data

```{r}
original_pk_long %>% mutate(group="original") %>% 
  bind_rows(ctgan_long %>% mutate(group="synthetic")) %>% 
              ggplot(aes(x = time, y = DV, color = group)) + geom_point() +
  geom_point(alpha = 0.2, size = 3) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw()


original_pk_long %>% mutate(group="original") %>% 
  bind_rows(ctgan_long %>% 
              mutate(group="synthetic")) %>% 
  mutate(id = as.factor(id)) %>% 
  ggplot(aes(x = time, y = log(DV), color = id)) +  geom_line(show.legend = FALSE)+
  geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
  labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
  theme_bw() + facet_wrap(~group)
```


Export long and wide
```{r}
write_csv(ctgan_long, file = "tacro_coeur_synthetic_ctgan.csv")
write_csv(ctgan, file = "wide_tacro_coeur_synthetic_ctgan.csv")

```

## Augmented data

### load the data

```{r}
# ctgan_augmented <- read_csv("GAN_sortie_anonymisation240108/pkpop_ctgan_data_large_v240108.dat")
```


### summary distribution
```{r}
# summary(ctgan_augmented)
# summary(original_pk)
```

Plot relationship C0 and CYP3A5

```{r}
# original_pk %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
#   geom_boxplot() +
#   labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Original") +
#   theme_bw()
# 
# ctgan_augmented %>% ggplot(aes(x = as.factor(CYP3A5), y =conc_0)) +
#   geom_boxplot() +
#   labs(y = "C0 tacrolimus (mg/L)", x = "CYP3A5 status", title = "Synthetic") +
#   theme_bw()
```


### plot correlation
```{r}

# ##Correlation Analysis
#   cor_real <- cor(original_pk, use = "complete.obs")
#   cor_synthetic <- cor(ctgan_augmented %>% select(-SEX), use = "complete.obs")
#   
# # plots
# ggcorrplot(cor_real, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
# # plots
# ggcorrplot(cor_synthetic, hc.order = TRUE, type = "lower",
#            lab = TRUE,  pch.cex = 5,
#   tl.cex = 6, lab_size = 2)
```

Graphical exploration of distribution

```{r}
# group_comparison <-
#    original_pk %>% 
#   mutate(group="original") %>% 
#   bind_rows(ctgan_augmented %>% 
#               mutate(group="synthetic")) 
# 
# pm <- group_comparison %>% ggpairs(
#   ggplot2::aes(colour = group,alpha = 0.5),
#   upper = list(continuous = wrap("cor", size = 1.5)),
#   lower=list(combo=wrap("facethist", binwidth=0.5))) + 
#   theme(strip.text.x = element_text(size = 5),
#            strip.text.y = element_text(size = 5),axis.text = element_text(size = 5))
# pm
# ggsave("comparaison_distribution_PK_ctgan_augmented.pdf")

```

Process and plot the data

```{r}
# ctgan_augmented_long <- ctgan_augmented %>%
#   mutate(id = 1:nrow(ctgan_augmented)) %>% 
#   pivot_longer(cols = starts_with("conc_"), names_to = "time", values_to = "DV", names_prefix = "conc_") %>%
#   mutate(time = as.numeric(time)) %>% 
#   arrange(id, time) %>% 
#   relocate(id)

```

Plot the data

```{r}
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(ctgan_augmented_long %>% mutate(group="synthetic")) %>% 
#               ggplot(aes(x = time, y = DV, color = group)) + geom_point() +
#   geom_point(alpha = 0.2, size = 3) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw()
# 
# 
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(ctgan_augmented_long %>% 
#               mutate(group="synthetic")) %>% 
#   mutate(id = as.factor(id)) %>% 
#   ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
#   geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw() + facet_wrap(~group)
```


Export long and wide
```{r}
# write_csv(ctgan_augmented_long, file = "tacro_coeur_synthetic_ctgan_augmented.csv")
# write_csv(ctgan_augmented, file = "wide_tacro_coeur_synthetic_ctgan_augmented.csv")

```


## global spahghetti plot tacro and dapto

```{r}
original_pk_long %>% mutate(group="original") %>%
  bind_rows(avatar_knn5 %>%
              mutate(group="Avatar_knn5")) %>%
    bind_rows(avatar_knn15 %>%
              mutate(group="Avatar_knn15")) %>%
    bind_rows(tvae_long %>%
              mutate(group="TVAE")) %>%
    bind_rows(ctgan_long %>%
              mutate(group="CTGAN")) %>%
  mutate(id = as.factor(id)) %>%
  ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
  geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
  labs(x = "Time (h)", y = "Tacrolimus concentration(mg/L)")+
  theme_bw() + facet_wrap(~group) +
  scale_x_continuous(
    limits = c(0, 12),            # Set x-axis limits
    breaks = seq(0, 12, by = 2)   # Set x-axis ticks every 2 hours
  ) +
  global_spaghetti_plot_dapto +
  plot_annotation(tag_levels = 'A')
ggsave("Figure1.pdf")
```

```{r}
# previous version
# original_pk_long %>% mutate(group="original") %>% 
#   bind_rows(avatar_knn5 %>% 
#               mutate(group="Avatar_knn5")) %>% 
#     bind_rows(avatar_knn15 %>% 
#               mutate(group="Avatar_knn15")) %>% 
#     bind_rows(avatar_augmented_knn5 %>% 
#               mutate(group="Avatar_augmented_knn5")) %>% 
#       bind_rows(avatar_augmented_knn15 %>% 
#               mutate(group="Avatar_augmented_knn15")) %>% 
#     bind_rows(tvae_long %>% 
#               mutate(group="TVAE")) %>% 
#     bind_rows(tvae_augmented_long %>% 
#               mutate(group="TVAE_augmented")) %>%
#     bind_rows(ctgan_long %>% 
#               mutate(group="CTGAN")) %>%
#     bind_rows(ctgan_augmented_long %>% 
#               mutate(group="CTGAN_augmented")) %>%
#   mutate(id = as.factor(id)) %>% 
#   ggplot(aes(x = time, y = DV, color = id)) +  geom_line(show.legend = FALSE)+
#   geom_point(alpha = 0.2, size = 3, show.legend = FALSE) +
#   labs(x = "Time (h)", y = "tacrolimus concentration(mg/L)")+
#   theme_bw() + facet_wrap(~group)
# ggsave("Figure1.pdf")
```

# table one

grouped data

```{r}
grouped_data <- original_pk %>% mutate(group="original") %>% 
  bind_rows(avatars_tibble_knn5 %>% 
              mutate(group="Avatar_knn5")) %>% 
    bind_rows(avatars_tibble_knn15 %>% 
              mutate(group="Avatar_knn15")) %>% 
    # bind_rows(augmented_data_5 %>% 
    #           mutate(group="Avatar_augmented_knn5")) %>% 
    #   bind_rows(augmented_data_15 %>% 
              # mutate(group="Avatar_augmented_knn15")) %>% 
    bind_rows(tvae %>% 
              mutate(group="TVAE")) %>% 
    # bind_rows(tvae_augmented %>% 
    #           mutate(group="TVAE_augmented")) %>%
    bind_rows(ctgan %>% 
              mutate(group="CTGAN")) 
    # bind_rows(ctgan_augmented %>% 
    #           mutate(group="CTGAN_augmented"))
```


## Summary of the 2 datasets
```{r}
library(tableone)
## Vector of categorical variables that need transformation
catVars <- c("Visite","SEX", "CYP3A5")
## Create a variable list.
vars <- c("Visite", "DOSE", "AGE", "SEX", "HT", "CYP3A5", "conc_0", "conc_0.33", 
"conc_1", "conc_1.5", "conc_3", "conc_4", "conc_6", "conc_8", 
"conc_9", "conc_12", "conc_0.66", "conc_2")
tableOne <- CreateTableOne(vars = vars, strata = "group",factorVars = catVars, data = grouped_data)
tableOne2<-print(tableOne, nonnormal = c( "DOSE", "AGE", "HT", "conc_0", "conc_0.33", 
"conc_1", "conc_1.5", "conc_3", "conc_4", "conc_6", "conc_8", 
"conc_9", "conc_12", "conc_0.66", "conc_2"), printToggle=F, minMax=T)
```

```{r , echo=F}
kableone(tableOne2)
```

